Cooperative Control for Narrow Passage Traversal with an Ornithopter Micro Air Vehicle and Lightweight Ground Station

### 2012-10-10 manuscript.tex
New figures and some text additions

%----------------------------------------------------------------------------%
\subsection{Ornithopter Flight Control}
%TODO(cameron)
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}

@@

@@

>>>>

%----------------------------------------------------------------------------%
\subsection{Ornithopter Flight Control}
\label{sec:flight_control}
%TODO(cameron)
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}

We determined the turning speed and turning radius of the H$^2$Bird experimentally using the response of the system to the input of a 90 degree turn to the right. The results of this experiment are depicted in Figure \ref{fig:step_response}. The data for the experiment was gathered from the gyro data integrated on-board the H$^2$Bird. We used Matlab to fit a simple low-order model, $H(s) = \frac{0.94782}{1+0.61998s}$, of the turning system to the step response with the physical heading as the state and the heading setpoint as the input. We use this model in Section X to determine the backwards reachable set for navigating through the window in simulation.

The step response exhibits a rise time of approximately 1.4 seconds. The H$^2$Bird flies at an average forward velocity of 1.2 m/s, so the estimated minimum turning radius of the robot is 1.07 meters.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{figure}

@@

We determined the backwards reachable set of initial states for sussessful window traversal both geometrically and in simulation. The results are shown in Figure X. The geometrically infeasible region is indicated in blue and was computed using the minimum turning radius and simple geometery. Both the regions in red and blue indicate the infeasible region determined in simulation. We executed the simulation on the fitted turning model described in Section \ref{sec:flight_control}, with a PID controller steering the system to the center of the window as the input. The infeasible region calculated in simulation is a superset of the geometrically infeasible region, and is closer to the true infeasible region of the real system.

The
